Methodology for Assessing the State of the Practice for Domain X

### 2020-04-15 StateOfPractice/Methodology/GradingTemplate.tex
Hard wrap with to 80

The table below lists the full set of measures that are assessed for each
software product.  The measures are grouped under headings for each quality, and
one for summary information.  Following each measure, the type for a valid
result is given in brackets.  Many of the types are given as enumerated sets.
For instance, the response on many of the questions is one of ``yes,'' ``no,''
or ``unclear.''  The type ``number'' means natural number, a positive integer.  The
types for date and url are not explicitly defined, but they are what one would
expect from their names.  In some cases the response for a given question is not
necessarily limited to one answer, such as the question on what platforms are
supported by the software product.  Case like this are indicated by ``set of''
preceding the type of an individual answer.  The type in these cases are then
the power set of the individual response type.  In some cases a superscript $^*$
is used to indicate that a response of this type should be accompanied by
explanatory text.  For instance, if problems were caused by uninstall, the
reviewer should note what problems were caused.

@@

  Are there installation instructions? (\{yes, no\})\\
  Are the installation instructions linear? (\{yes, no, n/a\})\\
  Is there something in place to automate the installation? (\{yes$^*$, no\})\\
  Is there a specified way to validate the installation, such as a test suite? \ad{What's the difference between this one and the getting started tutorial?} (\{yes$^*$, no\})\\
  How many steps were involved in the installation? (number) \ad{what if the installation has different steps on different OS?}\\
  How many software packages need to be installed before or during installation?
  (number) \ad{should it be 0 if no packages needed? I saw some answers with "no" or "none"}\\
  Run uninstall, if available. Were any obvious problems caused? (\{unavail, yes$^*$, no\})\\
  Overall impression? (\{1 .. 10\})\\

>>>>

The table below lists the full set of measures that are assessed for each
software product. The measures are grouped under headings for each quality,
an done for summary information. Following each measure, the type for a valid
result is given in brackets.  Many of the types are given as enumerated sets.
For instance, the response on many of the questions is one of ``yes,'' ``no,''
or ``unclear.'' The type ``number'' means natural number, a positive integer.
The
types for date and url are not explicitly defined, but they are what one would
expect from their names. In some cases the response for a given question is
not necessarily limited to one answer, such as the question on what platforms are
supported by the software product.  Case like this are indicated by ``set of''
preceding the type of an individual answer.  The type in these cases are then
the power set of the individual response type. In some cases a superscript
$^*$is used to indicate that a response of this type should be accompanied by
explanatory text.  For instance, if problems were caused by uninstall, the
reviewer should note what problems were caused.

@@

  Are there installation instructions? (\{yes, no\})\\
  Are the installation instructions linear? (\{yes, no, n/a\})\\
  Is there something in place to automate the installation? (\{yes$^*$, no\})\\
Is there a specified way to validate the installation, such as a test suite?
\ad{What's the difference between this one and the getting started tutorial?}
(\{yes$^*$, no\})\\
How many steps were involved in the installation? (number) \ad{what if the
installation has different steps on different OS?}\\
How many software packages need to be installed before or during
installation?(number) \ad{should it be 0 if no packages needed? I saw some
answers with "no"
or "none"}\\
Run uninstall, if available. Were any obvious problems caused? (\{unavail,
yes$^*$, no\})\\
  Overall impression? (\{1 .. 10\})\\
